\mythesistitle

### 2011-11-27 src/synopsis.tex
sec 4/sumary of results is almost done.

\section{Summary of results}
\label{sec:results}
\vspace{\secfirstparatrim}
% We address the computation of TPL\footnote{Tree Path Labeling} for a
% given hypergraph\footnote{The term {\em hypergraph} is used instead
%   {\em set systems} are used interchangably in this
%   section. Hypergraphs that have TPLs on some target tree are called
%   {\em path hypergraphs}.} and target tree in this research. However
% optimization problems in TPL, akin to problems in
% Section~\ref{sec:optcop} for COP, is outside the scope of this thesis.
As we saw earlier by the result in \cite{nsnrs09}, pairwise
intersection cardinality preservation is necessary and sufficient for
an interval assignment to be feasible for a given
hypergraph\footnote{A {\em hypergraph} is an alternate representation
  of a set system and will be used through out this section.} and thus
is a characterization for COP. In our work we extend this
characterization and find that trio-wise intersection cardinality
preservation makes a tree path labeling (TPL) feasible, which is a
generalization of the COP problem. This problem, {\FTPL}\footnote{A
  {\em tree path labeling} $\cl$ is a bijection of paths from the
  target tree $T$ to the hyperedges in given hypergraph $\cF$.}, is
defined as follows.

%\begin{tabular}[t]{c}
{\small
\begin{minipage}[h]{5in}
 % \begin{singlespace}
 \vspace{2mm}
 {\large \FTPL}\\
 \begin{tabular}[t]{l|l}
 \hline\\
    {\tt Input} & 
    \begin{minipage}[t]{\probdefwidth}
      A hypergraph $\cF$ with vertex set $U$, a tree $T$ and a
      bijection $\cl$~$:$~$\cF \rightarrow \cP$, where $\cP$ is a set
      of paths from $T$.\\
    \end{minipage}\\
    {\tt Question} &
    \begin{minipage}[t]{\probdefwidth}
      Does there exist a bijection $\phi$~$:$~$U \rightarrow V(T)$
      such that $\phi$ when applied on any hyperedge in $\cF$ will
      give
      the path mapped to it by the given tree path labeling $\cl$.\\
      { i.e., $\cl(S) = \{\phi(x) \mid x \in S\}$, for every hyperedge
        $S \in \cF$.}
    \end{minipage}\\
  \end{tabular}
  % \end{singlespace}
\end{minipage}\\
}
%\end{tabular}

We give a necessary and sufficient condition for {\FTPL} to output in
affirmative. This characterization can be checked in polynomial time.
The most interesting consequence is that in our constructive
procedure, it is sufficient to iteratively check if three-way
intersection cardinalities are preserved.  In other words, in each
iteration, it is sufficient to check if the intersection of any three
hyperedges is of the same cardinality as the intersection of the
corresponding paths.  Thus this generalizes the well studied question
of the feasible interval assignment problem which is the special case
when the target tree $T$ is simply a path \cite{wlh02,nsnrs09}.

@@

    {\tt Question} &
    \begin{minipage}[t]{\probdefwidth}
      Does there exist a set of paths $\cP$ from $T$ and a bijection
      $\cl$~$:$~$\cF \rightarrow \cP$, such that {\FTPL} returns {\bf
        true} on $(\cF, T, \cl)$.
    \end{minipage}\\
  \end{tabular}
  % \end{singlespace}
\end{minipage}\\
}
\def \CFTPLKTREE {\sc Compute $k$-subdivided Star Path Labeling}

We present a polynomial time algorithm for {\CFTPL} when the target
tree $T$ belongs to a special class of trees called {\em
  $k$-subdivided stars} and when the hyperedges in the hypergraph
$\cF$ have at most $k+2$ vertices. The examples of $k$-subdivided
stars are given in Figure~\ref{fig:ksubstar}.

%This problem, {\CFTPLKTREE}, is defined as follows. \\
\begin{figure}[t]
  \centering
  \begin{tabular}[h]{ccccc}
  \includegraphics[scale=0.3]{../img/star.pdf} &&&&
  \includegraphics[scale=0.3]{../img/kstar.pdf}\\
  (a) &&&& (b)
  \end{tabular}
  \caption{\figtabsize Examples of $k$-subdivided stars. (a) $k = 0$
    (b) $k = 2$ }
  \label{fig:ksubstar}
\end{figure}

%\vspace{3mm}
{\small
\begin{minipage}[h]{5in}
 % \begin{singlespace}
 \vspace{2mm}
  {\large \CFTPLKTREE}\\
  \begin{tabular}[t]{l|l}
    \hline\\
    {\tt Input} & 
    \begin{minipage}[t]{\probdefwidth}
      A hypergraph $\cF$ with vertex set $U$ such that every hyperedge
      $S \in \cF$ is of cardinality atmost $k+2$ and a $k$-subdivided
      star $T$.\\
    \end{minipage}\\
    {\tt Question} &
    \begin{minipage}[t]{\probdefwidth}
      Does there exist a set of paths $\cP$ from $T$ and a bijection
      $\cl$~$:$~$\cF \rightarrow \cP$, such that {\FTPL} returns {\bf
        true} on $(\cF, T, \cl)$.
    \end{minipage}\\
  \end{tabular}
  % \end{singlespace}
\end{minipage}\\
}

In spite of this being a restricted case, we believe that our results
are of significant interest in understanding the nature of {\sc Graph
  Isomorphism} which is polynomial time solvable in interval graphs
while being hard on path graphs\cite{kklv10}.

\tnote{give gyan on why ktree is so.}

>>>>

\section{Summary of results}
\label{sec:results}
\vspace{\secfirstparatrim}
% We address the computation of TPL\footnote{Tree Path Labeling} for a
% given hypergraph\footnote{The term {\em hypergraph} is used instead
%   {\em set systems} are used interchangably in this
%   section. Hypergraphs that have TPLs on some target tree are called
%   {\em path hypergraphs}.} and target tree in this research. However
% optimization problems in TPL, akin to problems in
% Section~\ref{sec:optcop} for COP, is outside the scope of this thesis.
As we saw earlier by the result in \cite{nsnrs09}, pairwise
intersection cardinality preservation is necessary and sufficient for
an interval assignment to be feasible for a given
hypergraph\footnote{A {\em hypergraph} is an alternate representation
  of a set system and will be used through out this section.} and thus
is a characterization for COP. In our work we extend this
characterization and find that trio-wise intersection cardinality
preservation makes a tree path labeling \footnote{A
  {\em tree path labeling} $\cl$ is a bijection of paths from the
  target tree $T$ to the hyperedges in given hypergraph $\cF$.} (TPL) feasible, which is a
generalization of the COP problem. This problem is
defined as follows.

%\begin{tabular}[t]{c}
{\small
\begin{minipage}[h]{5in}
 % \begin{singlespace}
 \vspace{2mm}
 {\large \FTPL}\\
 \begin{tabular}[t]{l|l}
 \hline\\
    {\tt Input} & 
    \begin{minipage}[t]{\probdefwidth}
      A hypergraph $\cF$ with vertex set $U$, a tree $T$, a set of
      paths $\cP$ from $T$ and a
      bijection $\cl$~$:$~$\cF \rightarrow \cP$.\\
    \end{minipage}\\
    {\tt Question} &
    \begin{minipage}[t]{\probdefwidth}
      Does there exist a bijection $\phi$~$:$~$U \rightarrow V(T)$
      such that $\phi$ when applied on any hyperedge in $\cF$ will
      give
      the path mapped to it by the given tree path labeling $\cl$.\\
      { i.e., $\cl(S) = \{\phi(x) \mid x \in S\}$, for every hyperedge
        $S \in \cF$.}
    \end{minipage}\\
  \end{tabular}
  % \end{singlespace}
\end{minipage}\\
}
%\end{tabular}

We give a necessary and sufficient condition (called ICPPL)\tnote{say a few
  words about icppl} for {\FTPL} to output in
affirmative. This characterization can be checked in polynomial time.
The most interesting consequence is that in our constructive
procedure, it is sufficient to iteratively check if three-way
intersection cardinalities are preserved.  In other words, in each
iteration, it is sufficient to check if the intersection of any three
hyperedges is of the same cardinality as the intersection of the
corresponding paths.  Thus this generalizes the well studied question
of the feasible interval assignment problem which is the special case
when the target tree $T$ is simply a path \cite{wlh02,nsnrs09}.

\tnote{A few lines on the algo itself.}

@@

    {\tt Question} &
    \begin{minipage}[t]{\probdefwidth}
      Does there exist a set of paths $\cP$ from $T$ and a bijection
      $\cl$~$:$~$\cF \rightarrow \cP$, such that {\FTPL} returns {\bf
        true} on $(\cF, T, \cl)$.
    \end{minipage}\\
  \end{tabular}
  % \end{singlespace}
\end{minipage}\\
}

\def \kstar {$k$-subdivided star}
\def \CFTPLKTREE {\sc Compute $k$-subdivided Star Path Labeling}

We present a polynomial time algorithm for {\CFTPL} when the target
tree $T$ belongs to a special class of trees called {\em \kstar s} and
when the hyperedges in the hypergraph $\cF$ have at most $k+2$
vertices. A couple of examples of {\kstar s} are given in
Figure~\ref{fig:ksubstar}.

%This problem, {\CFTPLKTREE}, is defined as follows. \\
\begin{figure}[t]
  \centering
  \begin{tabular}[h]{ccccc}
  \includegraphics[scale=0.3]{../img/star.pdf} &&&&
  \includegraphics[scale=0.3]{../img/kstar.pdf}\\
  (a) &&&& (b)
  \end{tabular}
  \caption{\figtabsize Examples of {\kstar s}. (a) $k = 0$
    (b) $k = 2$ }
  \label{fig:ksubstar}
\end{figure}

%\vspace{3mm}
{\small
\begin{minipage}[h]{5in}
 % \begin{singlespace}
 \vspace{2mm}
  {\large \CFTPLKTREE}\\
  \begin{tabular}[t]{l|l}
    \hline\\
    {\tt Input} & 
    \begin{minipage}[t]{\probdefwidth}
      A hypergraph $\cF$ with vertex set $U$ such that every hyperedge
      $S \in \cF$ is of cardinality atmost $k+2$ and a {\kstar} $T$.\\
    \end{minipage}\\
    {\tt Question} &
    \begin{minipage}[t]{\probdefwidth}
      Does there exist a set of paths $\cP$ from $T$ and a bijection
      $\cl$~$:$~$\cF \rightarrow \cP$, such that {\FTPL} returns {\bf
        true} on $(\cF, T, \cl)$.
    \end{minipage}\\
  \end{tabular}
  % \end{singlespace}
\end{minipage}\\
}

In spite of this being a restricted case, we believe that our results
are of significant interest in understanding the nature of {\sc Graph
  Isomorphism} which is polynomial time solvable in interval graphs
while being hard on path graphs\cite{kklv10}. {\kstar s} are a class
of trees which are in many ways very close to intervals or paths. Each
ray\footnote{The path from a leaf to the root, the vertex with highest
degree, is called a {\em ray} of the \kstar.} are independent except
for the root\footnote{The vertex with maximum degree in a {\kstar} is
  called {\em root}} and hence can be considered as an independent interval
till the root. Our algorithm builds on this fact and uses the interval
assignment algorithm\cite{nsnrs09} up until ``reaching'' the root and
then uses the trio-wise intersection cardinality (the extra condition
in ICPPL after ICPIA) check to resolve the
ambiguity about which ray the algorithm should ``grow'' the solution
into in the next iteration.
